\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles\\[1em] Supplementary material

### 2019-06-19 SuppMat.tex

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{inconsolata}

@@

\section{Detailed results on Cordero~\emph{et al} dataset}
\subsection{Structure prediction ordered by RNA}

 \Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}[H]
\centering
\newcommand{\B}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\BR}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\D}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\newcommand{\DR}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}lHHHHHHHHHHHHHHHH@{}}
 	\toprule
 	                              & \multicolumn{8}{l}{ \OurTool{}}                                     & \multicolumn{4}{l}{\Software{RNAfold} -- MFE mode} & \multicolumn{4}{l}{\Software{RNAfold} -- MEA mode}  \\
 	\textbf{CMCT}                 & \D    & \B    & \D       & \D    & \D    & \B       & \B    & \BR   & \D       & \D    & \B    & \DR                     & \D    & \D    & \B       & \D                       \\
 	\textbf{NMIA}                 & \D    & \D    & \B       & \D    & \B    & \D       & \B    & \BR   & \D       & \D    & \D    & \BR                     & \D    & \D    & \D       & \B                       \\
 	\textbf{DMS}                  & \D    & \D    & \D       & \B    & \B    & \B       & \D    & \BR   & \D       & \B    & \D    & \DR                     & \D    & \B    & \D       & \D                       \\ \midrule
 	5SRNA,E.Coli                  & 0.25  & 0.238 & 0.247    & 0.244 & 0.247 & 0.247    & 0.254 & 0.241 & 0.241    & 0.686 & 0.254 & 0.686                   & 0.241 & 0.686 & 0.269    & 0.686                    \\
 	glycineriboswitch,F.nucleatum & 0.568 & 0.627 & 0.868    & 0.952 & 0.868 & 0.658    & 0.868 & 0.868 & 0.306    & 0.313 & 0.395 & 0.313                   & 0.593 & 0.593 & 0.693    & 0.6                      \\
 	cidGMPriboswitch,V.Cholerae   & 0.654 & 0.77  & 0.654    & 0.77  & 0.654 & 0.77     & 0.654 & 0.77  & 0.77     & 0.77  & 0.667 & 0.77                    & 0.77  & 0.72  & 0.667    & 0.77                     \\
 	P4P6domain                    & 0.864 & 0.856 & 0.881    & 0.864 & 0.864 & 0.856    & 0.864 & 0.856 & 0.837    & 0.808 & 0.773 & 0.714                   & 0.845 & 0.808 & 0.781    & 0.722                    \\
 	adenineriboswitch,add         & 1     & 0.956 & 1        & 0.977 & 1     & 0.956    & 1     & 1     & 1        & 0.333 & 0.41  & 1                       & 1     & 0.333 & 0.356    & 0.306                    \\
 	tRNAphenylalanineyeast        & 0.286 & 0.746 & 0.976    & 0.746 & 0.976 & 0.746    & 0.976 & 0.976 & 0.976    & 0.976 & 0.976 & 0.976                   & 0.334 & 0.976 & 0.976    & 0.976                    \\ \midrule
 	Average                       & 0.604 & 0.7   & 0.77     & 0.76  & 0.77  & 0.705    & 0.77  & 0.785 & 0.69     & 0.65  & 0.58  & 0.74                    & 0.63  & 0.69  & 0.62     & 0.68                     \\ \bottomrule
 \end{tabular}
\end{adjustbox}
\caption{GM of the structures predicted with \OurTool{}, compared to predictions of \Software{RNAfold} in energy mimization (MFE) and accuracy maximization (MEA) modes.}
%( ref. $supplementary\_data/benchmark\_6RNAs$)}
\end{table}
\subsection{Reproducibility}
\begin{table}[H]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}\toprule
 &\multicolumn{3}{l}{ NMIA} & \multicolumn{3}{l}{ DMS} & \multicolumn{3}{l}{CMCT} &\multicolumn{3}{l}{ NMIA+DMS} & \multicolumn{3}{l}{ NMIA+CMCT} & \multicolumn{3}{l}{DMS+CMCT}& \multicolumn{3}{l}{NMIA+DMS+CMCT} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\

@@

\bottomrule
\end{tabular}
\end{adjustbox}
\caption{ GM of the predicted structures with \OurTool{} over 3 runs, in the presence of 1,2 and 3 sources of probing data}
%( ref. $supplementary\_data/benchmark\_6RNAs$)
\end{table}

\newpage

%\section{IPANEMAP Vs Rsample}
\section{Detailed results on Hadjin~\emph{et al} dataset}

 \begin{table}[h]

@@

\caption{Labels used for the 24 RNAs in the Hadjin \emph{ et al.} dataset~\cite{Hajdin2013}.}
\label{clyu}

@@

@@

\Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}[H]
{\centering \begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
\begin{tabular}{llllHllH}
	\toprule
	      &        & \multicolumn{3}{l}{\Software{Rsample}}    & \multicolumn{3}{l}{\Software{IPANEMAP}}   \\
	{RNA} & Length & Sensitivity & PPV    & \multicolumn1c{GM} & Sensitivity & PPV    & \multicolumn1c{GM} \\ \midrule
	A     & 34     & 0.625       & 1      & 0.791              & 0.625       & 1      & 0.791              \\
	B     & 530    & 0.6622      & 0.6203 & 0.641              & 0.8986      & 0.8062 & 0.851              \\
	C     & 301    & 0.03        & 0.0313 & 0.031              & 0.6         & 0.6    & 0.6                \\
	D     & 214    & 0.6349      & 0.6667 & 0.651              & 0.7302      & 0.8519 & 0.789              \\
	E     & 500    & 0.6382      & 0.7823 & 0.707              & 0.5263      & 0.5517 & 0.539              \\
	F     & 47     & 0.4         & 0.75   & 0.548              & 0.6         & 0.75   & 0.671              \\
	G     & 118    & 0.7179      & 0.8    & 0.758              & 0.7692      & 0.8333 & 0.801              \\
	H     & 76     & 0.4762      & 0.5556 & 0.514              & 0.7619      & 0.7619 & 0.762              \\
	I     & 155    & 0.6786      & 0.8261 & 0.749              & 0.9821      & 0.9821 & 0.982              \\
	J     & 79     & 0.7727      & 0.85   & 0.81               & 0.9545      & 0.875  & 0.914              \\
	K     & 71     & 1           & 1      & 1                  & 1           & 0.9545 & 0.977              \\
	L     & 66     & 0.5625      & 0.6923 & 0.624              & 0.625       & 0.7143 & 0.668              \\
	M     & 79     & 0.6538      & 0.8095 & 0.727              & 0.6538      & 0.68   & 0.667              \\
	N     & 120    & 0.2857      & 0.2632 & 0.274              & 0.9714      & 0.9189 & 0.945              \\
	O     & 97     & 0.9286      & 0.9286 & 0.929              & 0.9286      & 0.8966 & 0.912              \\
	P     & 511    & 0.9328      & 0.7762 & 0.851              & 0.8908      & 0.7681 & 0.827              \\
	Q     & 401    & 0.5826      & 0.5583 & 0.57               & 0.7304      & 0.75   & 0.74               \\
	R     & 425    & 0.8397      & 0.8271 & 0.833              & 0.9084      & 0.8815 & 0.895              \\
	S     & 336    & 0.5481      & 0.6129 & 0.58               & 0.8077      & 0.866  & 0.836              \\
	T     & 473    & 0.7986      & 0.7143 & 0.755              & 0.8819      & 0.8194 & 0.85               \\
	U     & 412    & 0.5379      & 0.6174 & 0.576              & 0.75        & 0.8462 & 0.797              \\
	V     & 75     & 0.619       & 0.6842 & 0.651              & 0.619       & 0.5652 & 0.591              \\
	W     & 174    & 0.8095      & 0.8644 & 0.836              & 0.8095      & 0.9808 & 0.891              \\
	X     & 154    & 0.875       & 0.913  & 0.894              & 0.875       & 0.913  & 0.894              \\ \bottomrule
\end{tabular}
\end{adjustbox}\\}

\caption{\OurTool~ prediction performance compared to \Software{Rsample} tool}
\end{table}

@@

\newpage 
\section{Detailed results of Lariat capping ribozyme from {\itshape Didymium iridis}}

\begin{table}[H]
 \Heatset{min=0.2,  
	max=.5,   
	max colour=BadCol, % colour at maximum
	min colour=Aquamarine3,      % colour at minimum
	Min colour=Aquamarine3, % colour for values below min
	Max colour=BadCol   % colour for values above max
}
\begin{center}
\begin{tabular}{lHH}\toprule
 & \multicolumn{2}{c}{Distance of reactivity}\\
Condition & \multicolumn1c{to prediction}&\multicolumn1c{to native}\\
\toprule
\OneMSevILUMg & 0.234 & 0.2872\\
\OneMSevILU &	0.2784 & 0.2961\\
\NMIAMg &	0.2606 & 0.2518\\
\NMIA &	0.2961 & 0.3316\\
\OneMSevILUThreeMg &	0.4291 & 0.3936\\
\NMIAMgCE &	0.4291 & 0.3404\\
\NAIMg 	& 0.3493 & 0.305\\
\BzCNMg & 	0.3759 & 0.2429\\
\OneMSevMgCE &	0.4379 & 0.3759\\
\CMCTMg &	0.4911 & 0.4113\\
\OneMSevILUThree &	0.2961 & 0.3404\\
\DMSMg &	0.3493 & 0.3227\\
\NMIACE 	&0.2695 &0.2518 \\
\OneMSevCE &	0.3582 & 	0.3316\\
\BzCN &	0.4911 & 	0.4734\\
\NAICE &	0.4025 &0.4025\\
\bottomrule
\end{tabular}
\end {center}
\caption{Distance of the predicted structure from the considered probing data.}
\end{table}

\begin{table}[H]
\newcommand{\MyScale}{.18}
\begin{adjustbox}{max width=\textwidth,keepaspectratio}
\begin{tabular}{@{}c|cccc@{}}

%\toprule
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/native_structure}&
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILU_NMIAMg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILUMg_1M7ILU3Mg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7MgCE_NMIAMgCE}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/NaiMg_CMCTMg}\\
 \midrule
Native&\OneMSevILU&\OneMSevILUMg&\OneMSevMgCE&\NAIMg\\
structure &+\NMIAMg&+\OneMSevILUThreeMg&+\NMIAMgCE&+\CMCTMg\\
\end{tabular}
\end{adjustbox}
\caption{Predicted structures with conditions belonging to the same cluster}
\end{table}

>>>>

%%% PAGE DIMENSIONS
\usepackage{geometry} % to change the page dimensions
\geometry{a4paper} % or letterpaper (US) or a5paper or....
 \geometry{margin=1in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{times}
\usepackage{inconsolata}

\usepackage{rotating}

@@

\section*{Multiprobing benchmark (Cordero~\emph{et al}~\cite{Cordero2012} dataset)}
\subsection*{Structure prediction ordered by RNA}

 \Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}
\begin{table}[H]
\centering
\newcommand{\B}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\BR}{\multicolumn{1}{c}{$\bullet$}}
\newcommand{\D}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\newcommand{\DR}{\multicolumn{1}{c}{\color{gray}$\circ$}}
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{@{}lHHHHHHHHHHHHHHHH@{}}
 	\toprule
 	                              & \multicolumn{8}{l}{ \OurTool{}}                                     & \multicolumn{4}{l}{\Software{RNAfold} -- MFE mode} & \multicolumn{4}{l}{\Software{RNAfold} -- MEA mode}  \\
 	\textbf{CMCT}                 & \D    & \B    & \D       & \D    & \D    & \B       & \B    & \BR   & \D       & \D    & \B    & \DR                     & \D    & \D    & \B       & \D                       \\
 	\textbf{NMIA}                 & \D    & \D    & \B       & \D    & \B    & \D       & \B    & \BR   & \D       & \D    & \D    & \BR                     & \D    & \D    & \D       & \B                       \\
 	\textbf{DMS}                  & \D    & \D    & \D       & \B    & \B    & \B       & \D    & \BR   & \D       & \B    & \D    & \DR                     & \D    & \B    & \D       & \D                       \\ \midrule
 	5SRNA,E.Coli                  & 0.25  & 0.238 & 0.247    & 0.244 & 0.247 & 0.247    & 0.254 & 0.241 & 0.241    & 0.686 & 0.254 & 0.686                   & 0.241 & 0.686 & 0.269    & 0.686                    \\
 	glycineriboswitch,F.nucleatum & 0.568 & 0.627 & 0.868    & 0.952 & 0.868 & 0.658    & 0.868 & 0.868 & 0.306    & 0.313 & 0.395 & 0.313                   & 0.593 & 0.593 & 0.693    & 0.6                      \\
 	cidGMPriboswitch,V.Cholerae   & 0.654 & 0.77  & 0.654    & 0.77  & 0.654 & 0.77     & 0.654 & 0.77  & 0.77     & 0.77  & 0.667 & 0.77                    & 0.77  & 0.72  & 0.667    & 0.77                     \\
 	P4P6domain                    & 0.864 & 0.856 & 0.881    & 0.864 & 0.864 & 0.856    & 0.864 & 0.856 & 0.837    & 0.808 & 0.773 & 0.714                   & 0.845 & 0.808 & 0.781    & 0.722                    \\
 	adenineriboswitch,add         & 1     & 0.956 & 1        & 0.977 & 1     & 0.956    & 1     & 1     & 1        & 0.333 & 0.41  & 1                       & 1     & 0.333 & 0.356    & 0.306                    \\
 	tRNAphenylalanineyeast        & 0.286 & 0.746 & 0.976    & 0.746 & 0.976 & 0.746    & 0.976 & 0.976 & 0.976    & 0.976 & 0.976 & 0.976                   & 0.334 & 0.976 & 0.976    & 0.976                    \\ \midrule
 	Average                       & 0.604 & 0.7   & 0.77     & 0.76  & 0.77  & 0.705    & 0.77  & 0.785 & 0.69     & 0.65  & 0.58  & 0.74                    & 0.63  & 0.69  & 0.62     & 0.68                     \\ \bottomrule
 \end{tabular}
\end{adjustbox}
\caption{GM of the structures predicted with \OurTool{}, compared to predictions of \Software{RNAfold} in energy mimization (MFE) and accuracy maximization (MEA) modes.}
%( ref. $supplementary\_data/benchmark\_6RNAs$)}
\end{table}
\subsection*{Stablity analysis}
\begin{table}[H]
\centering
\begin{adjustbox}{max width=1\textwidth}
 \begin{tabular}{lHHHHHHHHHHHHHHHHHHHHH}\toprule
 &\multicolumn{3}{l}{ NMIA} & \multicolumn{3}{l}{ DMS} & \multicolumn{3}{l}{CMCT} &\multicolumn{3}{l}{ NMIA+DMS} & \multicolumn{3}{l}{ NMIA+CMCT} & \multicolumn{3}{l}{DMS+CMCT}& \multicolumn{3}{l}{NMIA+DMS+CMCT} \\
% & \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM }& \multicolumn{3}{l}{ GM }  & \multicolumn{3}{l}{ GM } & \multicolumn{3}{l}{ GM } &\multicolumn{3}{l}{ GM }\\

@@

\bottomrule
\end{tabular}
\end{adjustbox}
\caption{GM of \OurTool predictions over three consecutive runs from up 3 sources of probing data.}
%( ref. $supplementary\_data/benchmark\_6RNAs$)
\end{table}

%\section{IPANEMAP Vs Rsample}
\section*{Mono probing benchmark (Hadjin~\emph{et al}~\cite{Hajdin2013} dataset)}

@@

\caption{Labels used as shorthands for the 24 RNAs in the Hadjin \emph{ et al.} dataset~\cite{Hajdin2013}.}
\label{clyu}

@@

\subsection*{Detailed results of \OurTool{} and \Software{Rsample}}
\begin{table}[H]
	{\centering \begin{adjustbox}{max width=\textwidth,max totalheight=\textheight,keepaspectratio}
			\begin{tabular}{llllHllH}
				\toprule
				&        & \multicolumn{3}{l}{\Software{Rsample}}    & \multicolumn{3}{l}{\Software{IPANEMAP}}   \\
				{RNA} & Length & Sensitivity & PPV    & \multicolumn1c{GM} & Sensitivity & PPV    & \multicolumn1c{GM} \\ \midrule
				A     & 34     & 0.625       & 1      & 0.791              & 0.625       & 1      & 0.791              \\
				B     & 530    & 0.6622      & 0.6203 & 0.641              & 0.8986      & 0.8062 & 0.851              \\
				C     & 301    & 0.03        & 0.0313 & 0.031              & 0.6         & 0.6    & 0.6                \\
				D     & 214    & 0.6349      & 0.6667 & 0.651              & 0.7302      & 0.8519 & 0.789              \\
				E     & 500    & 0.6382      & 0.7823 & 0.707              & 0.5263      & 0.5517 & 0.539              \\
				F     & 47     & 0.4         & 0.75   & 0.548              & 0.6         & 0.75   & 0.671              \\
				G     & 118    & 0.7179      & 0.8    & 0.758              & 0.7692      & 0.8333 & 0.801              \\
				H     & 76     & 0.4762      & 0.5556 & 0.514              & 0.7619      & 0.7619 & 0.762              \\
				I     & 155    & 0.6786      & 0.8261 & 0.749              & 0.9821      & 0.9821 & 0.982              \\
				J     & 79     & 0.7727      & 0.85   & 0.81               & 0.9545      & 0.875  & 0.914              \\
				K     & 71     & 1           & 1      & 1                  & 1           & 0.9545 & 0.977              \\
				L     & 66     & 0.5625      & 0.6923 & 0.624              & 0.625       & 0.7143 & 0.668              \\
				M     & 79     & 0.6538      & 0.8095 & 0.727              & 0.6538      & 0.68   & 0.667              \\
				N     & 120    & 0.2857      & 0.2632 & 0.274              & 0.9714      & 0.9189 & 0.945              \\
				O     & 97     & 0.9286      & 0.9286 & 0.929              & 0.9286      & 0.8966 & 0.912              \\
				P     & 511    & 0.9328      & 0.7762 & 0.851              & 0.8908      & 0.7681 & 0.827              \\
				Q     & 401    & 0.5826      & 0.5583 & 0.57               & 0.7304      & 0.75   & 0.74               \\
				R     & 425    & 0.8397      & 0.8271 & 0.833              & 0.9084      & 0.8815 & 0.895              \\
				S     & 336    & 0.5481      & 0.6129 & 0.58               & 0.8077      & 0.866  & 0.836              \\
				T     & 473    & 0.7986      & 0.7143 & 0.755              & 0.8819      & 0.8194 & 0.85               \\
				U     & 412    & 0.5379      & 0.6174 & 0.576              & 0.75        & 0.8462 & 0.797              \\
				V     & 75     & 0.619       & 0.6842 & 0.651              & 0.619       & 0.5652 & 0.591              \\
				W     & 174    & 0.8095      & 0.8644 & 0.836              & 0.8095      & 0.9808 & 0.891              \\
				X     & 154    & 0.875       & 0.913  & 0.894              & 0.875       & 0.913  & 0.894              \\ \bottomrule
			\end{tabular}
		\end{adjustbox}\\}
\caption{\OurTool~ prediction performance compared to \Software{Rsample} tool}
\end{table}

\subsection*{Stability analysis}

@@

\Heatset{min=0.4,  
	max=1,   
	max colour=Aquamarine3, % colour at maximum
	min colour=BadCol,      % colour at minimum
	Min colour=BadCol, % colour for values below min
	Max colour=Aquamarine3   % colour for values above max
}

@@

\section*{Case-study: Lariat capping ribozyme of {\itshape Didymium iridis}}
\subsection*{Compatibility of accessibility profiles with native and predicted structures}
\begin{table}[H]
 \Heatset{min=0.2,  
	max=.5,   
	max colour=BadCol, % colour at maximum
	min colour=Aquamarine3,      % colour at minimum
	Min colour=Aquamarine3, % colour for values below min
	Max colour=BadCol   % colour for values above max
}
\begin{center}
\begin{tabular}{lHH}\toprule
 & \multicolumn{2}{c}{Distance of reactivity}\\
Condition & \multicolumn1c{to prediction}&\multicolumn1c{to native}\\
\toprule
\OneMSevILUMg & 0.234 & 0.2872\\
\OneMSevILU &	0.2784 & 0.2961\\
\NMIAMg &	0.2606 & 0.2518\\
\NMIA &	0.2961 & 0.3316\\
\OneMSevILUThreeMg &	0.4291 & 0.3936\\
\NMIAMgCE &	0.4291 & 0.3404\\
\NAIMg 	& 0.3493 & 0.305\\
\BzCNMg & 	0.3759 & 0.2429\\
\OneMSevMgCE &	0.4379 & 0.3759\\
\CMCTMg &	0.4911 & 0.4113\\
\OneMSevILUThree &	0.2961 & 0.3404\\
\DMSMg &	0.3493 & 0.3227\\
\NMIACE 	&0.2695 &0.2518 \\
\OneMSevCE &	0.3582 & 	0.3316\\
\BzCN &	0.4911 & 	0.4734\\
\NAICE &	0.4025 &0.4025\\
\bottomrule
\end{tabular}
\end {center}
\caption{Distance of the predicted structure from the considered probing data.}
\end{table}

\begin{sidewaysfigure}
\newcommand{\MyScale}{.26}

{\centering
	\begin{adjustbox}{max width=\textwidth,max height=\textheight,keepaspectratio}
\begin{tabular}{@{}c|cccc@{}}

%\toprule
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/native_structure}&
 \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILU_NMIAMg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7ILUMg_1M7ILU3Mg}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/1M7MgCE_NMIAMgCE}& \includegraphics[scale=\MyScale]{graphs/Supp_structures/NaiMg_CMCTMg}\\
 \midrule
Native&\OneMSevILU&\OneMSevILUMg&\OneMSevMgCE&\NAIMg\\
structure &+\NMIAMg&+\OneMSevILUThreeMg&+\NMIAMgCE&+\CMCTMg\\
\end{tabular}
\end{adjustbox}\\}

\caption{Predicted structures with conditions belonging to the same cluster}
\end{sidewaysfigure}
